A new machine-learning-based prediction of survival in patients with end-stage liver disease

### 2022-12-01 analysis/article.Rmd
fix: missing linebreak

$$
\begin{aligned}
MELD3 = 1.33 (if female) &+
        4.56 &* \ln(bilirubin [mg/dL]) +  \\
        0.82 &* (137 - Na [mmol/L]) - 0.24 * (137 - Na [mmol/L]) * \ln(bilirubin [mg/dL]) + \\
        9.09 &* \ln(INR) + \\
        11.14 &* \ln(creatinine [mg/dL]) + 1.85 * (3.5 - albumin [g/dL]) - 1.83 * (3.5 - albumin [g/dL]) * \ln(creatinine [mg/dL]) + 6
\end{aligned}
$$
In contrast to MELD-Na the maximum allowed creatinine was set to 3.0 mg/dL.

>>>>

$$
\begin{aligned}
MELD3 = 1.33 (if female) &+ \\
        4.56 &* \ln(bilirubin [mg/dL]) +  \\
        0.82 &* (137 - Na [mmol/L]) - 0.24 * (137 - Na [mmol/L]) * \ln(bilirubin [mg/dL]) + \\
        9.09 &* \ln(INR) + \\
        11.14 &* \ln(creatinine [mg/dL]) + \\
        1.85 &* (3.5 - albumin [g/dL]) - 1.83 * (3.5 - albumin [g/dL]) * \ln(creatinine [mg/dL]) + 6
\end{aligned}
$$
In contrast to MELD-Na the maximum allowed creatinine was set to 3.0 mg/dL.
